---
title: "Time Machine in a 1920’s Motor Vehicle"
author: "koraxus"
date: "1/25/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background

Suppose you were able to turn a 1920's motor vehicle into a time machine.
It is of paramount importance to be able to properly estimate stopping distance at various speeds.

## Why is proper distance estimation important?

In the Back To The Future Movie, Dr. Brown does not adequately calculate stopping distance and the results are:

- Marty McFly crashes into a barn after traveling back in time
- Marty McFly crashes into a movie theater after traveling forward in time.

A stopping distance calculator will enable time travelers to properly plan travel.
At 88 mph, the flux capacitor activates time travel.


## Predicted Stopping Distance vs Speed

```{r cars, echo = FALSE}
model1<-lm(dist ~ speed, data= cars)
plot(cars$speed, mtcars$dist, xlab = "Speed (mph)",
         ylab= "Stopping Distance (ft)", bty="n", pch=16,
         xlim =  c(10, 150), ylim = c(50,1000))
abline(model1, col="red", lwd=2)
abline(v=88, col="blue", lwd=3)
```

## Thank You



